\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species

### 2024-01-29 ms.Rnw

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{Sweave}
\bibliographystyle{apalike}
\newcommand{\blind}{1}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}
\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

@@

<<Setup, include=FALSE,echo=FALSE,results=hide>>=
 library(plyr)
 library(reshape2)
 library(magrittr)
 library(foreach)
 library(readxl)
 library(doParallel)
 registerDoParallel(cores=36)
 library(pomp)
 library(panelPomp)
 library(ggplot2)

@@

\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align='center', fig=TRUE, width=14, height=4>>=  
   mixed_nopara_data_combined <- do.call(rbind, lapply(1:length(mixed_nopara_data), function(i) {
     cbind(mixed_nopara_data[[i]], group=paste("Trial", trails[i]))
   }))

 ggplot(mixed_nopara_data_combined, aes(x=day)) + 
   geom_line(aes(y=dent.adult, group=interaction(group, "dent.adult"))) + 
   geom_line(aes(y=lum.adult, color="blue", group=interaction(group, "lum.adult"))) +
   scale_x_continuous(limits = c(0, 52)) +
   scale_y_continuous(limits = c(0, 175)) +
   facet_grid(. ~ group, scales = "free", space = "free") +
   theme(
     strip.text = element_text(size=10),
     axis.text.x=element_text(color="black"),
     axis.ticks.x=element_line(color="black"),
     axis.text.y=element_text(color="black"),
     axis.ticks.y=element_line(color="black"),
     axis.title.x=element_blank(),
     axis.title.y=element_blank(),
     legend.position="none",
     panel.spacing = unit(0, "lines"), # Adjust spacing between panels
     strip.background = element_blank(), # Optional: Remove facet label background
     strip.placement = "outside"
   ) +
   labs(title="Daphnia density in Non-parasitized Dynamics") +
   guides(colour=guide_legend(title="Species"))
@
\caption{Plot of density of hosts in dynamics including both native and invasive host species of Daphnia. The trail A to J represents different buckets in the experiment}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=  
   mixed_para_data_combined <- do.call(rbind, lapply(1:length(mixed_para_data), function(i) {
     cbind(mixed_para_data[[i]], group=paste("Trial", trails[i]))
   }))

@@

<<Setup, include=FALSE,echo=FALSE,results=hide>>=
 load('all_shared.RData')

@@

\section{Results}
\label{sec:res}
<<Setup, include=FALSE,echo=FALSE,results=hide>>=
 load('SIRPF_model_estimate.RData')

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
%\usepackage{Sweave}
\bibliographystyle{apalike}
\newcommand{\blind}{1}

@@

\begin{document}
%\SweaveOpts{concordance=TRUE}
\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

@@

<<Setup,include=FALSE,echo=FALSE,results="hide">>=
 library(plyr)
 library(reshape2)
 library(magrittr)
 library(foreach)
 library(readxl)
 library(doParallel)
 registerDoParallel(cores=36)
 library(pomp)
 library(panelPomp)
 library(ggplot2)

@@

\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align="center", fig.width=14, fig.height=4>>=  
   mixed_nopara_data_combined <- do.call(rbind, lapply(1:length(mixed_nopara_data), function(i) {
     cbind(mixed_nopara_data[[i]], group=paste("Trial", trails[i]))
   }))

 ggplot(mixed_nopara_data_combined, aes(x=day)) + 
   geom_line(aes(y=dent.adult, group=interaction(group, "dent.adult"))) + 
   geom_line(aes(y=lum.adult, color="blue", group=interaction(group, "lum.adult"))) +
   scale_x_continuous(limits = c(0, 52)) +
   scale_y_continuous(limits = c(0, 175)) +
   facet_grid(. ~ group, scales = "free", space = "free") +
   theme(
     strip.text = element_text(size=10),
     axis.text.x=element_text(color="black"),
     axis.ticks.x=element_line(color="black"),
     axis.text.y=element_text(color="black"),
     axis.ticks.y=element_line(color="black"),
     axis.title.x=element_blank(),
     axis.title.y=element_blank(),
     legend.position="none",
     panel.spacing = unit(0, "lines"), # Adjust spacing between panels
     strip.background = element_blank(), # Optional: Remove facet label background
     strip.placement = "outside"
   ) +
   labs(title="Daphnia density in Non-parasitized Dynamics") +
   guides(colour=guide_legend(title="Species"))
@
\caption{Plot of density of hosts in dynamics including both native and invasive host species of Daphnia. The trail A to J represents different buckets in the experiment}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig.width=14, fig.height=4>>=  
   mixed_para_data_combined <- do.call(rbind, lapply(1:length(mixed_para_data), function(i) {
     cbind(mixed_para_data[[i]], group=paste("Trial", trails[i]))
   }))

@@

<<Setup-params,include=FALSE,echo=FALSE,results="hide">>=
 load('all_shared.RData')

@@

\section{Results}
\label{sec:res}
<<Setup-results, include=FALSE,echo=FALSE,results="hide">>=
 load('SIRPF_model_estimate.RData')
